---
title: "Assignment5"
author: "Evans Muchiri"
date: "3/9/2021"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# install.packages("dplyr")
# install.packages("DT")
# install.packages("leaflet")
# install.packages("ggplotly")
# install.packages("plotly")
# install.packages("reshape")
# #source("https://.org/Lite.R")
# 
# # Default Install
# neuro_install('MRIcloudT1volumetrics')
# 
# 
#install.packages("devtools")
# require(devtools)
# devtools::install_github("bcaffo/MRIcloudT1volumetrics")


#install.packages("MRIcloudT1volumetrics")
# install.packages("tidyverse")
# install.packages("ggplot2")
# install.packages("Hmisc")
# install.packages("knitr")
# install.packages("d3heatmap")
# install.packages("flexdashboard")

#
library(DT)
library(leaflet)
library(shiny)
library(reshape)
library(MRIcloudT1volumetrics)
library(tidyverse)
library(ggplot2)
library(Hmisc)
library(plotly)
library(knitr)
# library(d3heatmap)
library(flexdashboard)
library(reshape)
# library(MRIcloudT1volumetrics)
library(tidyverse)
library(ggplot2)
library(Hmisc)


# 

```

## Assignment 5
## Question 1

1. Create a shiny app of your Hogwarts house progam from the previous HW. Submit both the code and a link to the published app on shinyapps.io

https://emuchiri.shinyapps.io/HogwartsTheHouseApp/

### Links to the Hogwarts House app

``` {r hogshiyny, eval=FALSE, message=FALSE}
https://emuchiri.shinyapps.io/HogwartsTheHouseApp/
  

```


2. Recreate your plots from the previous assignment, except the mosaic plots, as interactive plotly graphics. Submit the Rmarkdown document and the html document.

## Question 2 plot 1
``` {r plotlyplots, warning=FALSE, echo=TRUE, eval=TRUE, message=FALSE}

library(plotly)

ds4phbme_raw=("https://raw.githubusercontent.com/bcaffo/ds4ph-bme/master/data/classInterests.txt")
dat11=read.table(ds4phbme_raw, sep="", header=TRUE)
class(dat11)

summary(dat11)
table(dat11)

smry=dat11 %>% group_by(Program) %>% summarise(students_no=n())
smry2=dat11 %>% group_by(Year) %>% summarise(students_no=n())

smry
smry2



plot1=ggplot(smry, aes(x=Program,y=students_no, fill=Program))
# plot1+geom_count()
plot1=plot1+geom_bar(stat="identity")
plot4=ggplotly(plot1)

plot2=ggplot(smry2, aes(x=Year,y=students_no, fill=Year))
# plot2+geom_count()
plot2=plot2+geom_bar(stat="identity")
plot5=ggplotly(plot2)
plot4
plot5



```

## Question 2 plot 2

```{r ds4phbme5, eval=TRUE, echo=TRUE }
# install.packages("pandas")
# library(pandas)
 # ds4phbme5_raw=("https://raw.githubusercontent.com/jhu-advdatasci/2018/master/data/KFF/healthcare-spending.csv")
dat51=read.table(file="/cloud/project/healthcare-spending2.csv", sep="", header=TRUE)
 attach(dat51)
class(dat51)
dim(dat51)
colnames(dat51)

dat52=dat51 %>%select("Location", "X1991__Total.Health.Spending", "X1992__Total.Health.Spending", "X1993__Total.Health.Spending", "X1994__Total.Health.Spending", "X1995__Total.Health.Spending", "X1996__Total.Health.Spending", "X1997__Total.Health.Spending", "X1998__Total.Health.Spending", "X1999__Total.Health.Spending" , "X2000__Total.Health.Spending" , "X2001__Total.Health.Spending", "X2002__Total.Health.Spending", "X2003__Total.Health.Spending", "X2004__Total.Health.Spending", "X2005__Total.Health.Spending", "X2006__Total.Health.Spending", "X2007__Total.Health.Spending", "X2008__Total.Health.Spending", "X2009__Total.Health.Spending", "X2010__Total.Health.Spending", "X2011__Total.Health.Spending", "X2012__Total.Health.Spending", "X2013__Total.Health.Spending", "X2014__Total.Health.Spending")


dim(dat52)

healthcare_data=dat52[2:52,]
names(healthcare_data)=c("Locations", 1991:2014 )
healthcare_spending2=melt(healthcare_data, id.var="Locations")

names(healthcare_spending2)[names(healthcare_spending2)=="variable"] <- "Year"
names(healthcare_spending2)[names(healthcare_spending2)=="value"] <- "HealthSpending"
names(healthcare_spending2)


healthcare_spending3=as.data.frame(healthcare_spending2)
class(healthcare_spending3)
# 
# nlist=ncol(dat52)
# yearlyspending=dat52[,2:nlist]

# 
plot55=ggplot(healthcare_spending3, aes(x=Year, y=HealthSpending, color=Locations )) 

# gg_HealthCare = ggplot(HealthCare_data2Reshaped,aes(x=as.numeric(variable),y=value,color=State))

plot55=plot55+geom_line(aes(group=Locations))

plot55=plot55+geom_point()
plot55=plot55+theme(axis.text.x = element_text(angle = 90))


# plot55=plot55+ggtitle("Amount of Healthcare Spending")+ ylab("Health Care Spending")+xlab("Year")

plot56=ggplotly(plot55)
plot56

# lot1+ggplot(dat52, mapping=aes(x=dat52[ ,3], y=Location))+geom_point(aes(color=factor(Location)))
# 
# plot551



```

## Quesiton 2 plot 3

``` {r plotlyq6, eval=TRUE, echo=TRUE}
#install.packages("pandas")
# library(pandas)
# ds4phbme5_raw=("https://raw.githubusercontent.com/jhu-advdatasci/2018/master/data/KFF/healthcare-spending.csv")
dat51=read.table(file="/cloud/project/healthcare-spending2.csv", sep="", header=TRUE)
class(dat51)
dim(dat51)
colnames(dat51)

dat62=dat51 %>%select("Location", "X1991__Total.Health.Spending", "X1992__Total.Health.Spending", "X1993__Total.Health.Spending", "X1994__Total.Health.Spending", "X1995__Total.Health.Spending", "X1996__Total.Health.Spending", "X1997__Total.Health.Spending", "X1998__Total.Health.Spending", "X1999__Total.Health.Spending" , "X2000__Total.Health.Spending" , "X2001__Total.Health.Spending", "X2002__Total.Health.Spending", "X2003__Total.Health.Spending", "X2004__Total.Health.Spending", "X2005__Total.Health.Spending", "X2006__Total.Health.Spending", "X2007__Total.Health.Spending", "X2008__Total.Health.Spending", "X2009__Total.Health.Spending", "X2010__Total.Health.Spending", "X2011__Total.Health.Spending", "X2012__Total.Health.Spending", "X2013__Total.Health.Spending", "X2014__Total.Health.Spending")



rowmean_state=function (data_health) {
  as.matrix(data_health)
  nlists2=ncol(data_health)
  mean_state_spend=round(apply(data_health[,2:nlists2],1, mean),0)

  as.data.frame(mean_state_spend)
  Location2=data_health[,1]
  
  result=cbind(Location2, mean_state_spend)
as.data.frame(result)
  return(result)
}

mean_state_spending=as.data.frame(rowmean_state(dat62))
                                  
mean_state_spending2=mean_state_spending[2:52,]
dim(mean_state_spending2)

#   
#   dat62=dat62 %>% mean(as.integer(dat52[,2:ncol(dat52)])) %>% 
#   mutate(mean_spending=mean(dat52[,2:ncol(dat52)])) %>%
#   barplot(Location, mean_spending)
# 

plot611=ggplot(mean_state_spending2, aes(Location2,mean_state_spend, fill=Location2))
plot611=plot611+geom_bar(stat="identity")+labs(x="States", y="Mean Health Spend")
plot611=plot611+theme(axis.text.x = element_text(angle = 90))
#theme(axis.text.x = element_text(), axis.text.y = element_text())
plot612=ggplotly(plot611)
plot612


```


## Question 3
3. Create a shiny app where a user enters in their height and weight and it returns BMI. Allow them to enter height and weight in feet or meters and lbs or kgs. Submit both the code and a link to the hosted app.

https://emuchiri.shinyapps.io/BMICalc/


``` {r BMICalc, message=FALSE, eval=FALSE}
https://emuchiri.shinyapps.io/BMICalc/
  

```



## Question 5
5. Create a Rmd and then html document that displays a leaflet plot with a marker for your favorite place in Baltimore.


```{r plots_fav_Baltimore, echo=TRUE, warning=FALSE }

library(leaflet)
# spdf<-geojson_read("C:\\unhcr\\Statistics_Data_Officer\\response\\america_adm1.geojson", what="sp")


walters_art=leaflet() %>%
  addTiles() %>%
  addMarkers(lat=39.324910, lng=-76.619500, 
             popup="Walters Art Gallery")
walters_art



```


## Question 4
4. Create a flexdashboard app that uses the kirby21 data from the previous assigment. In the left panel the user can select the type and level (1 to 3) and in the right hand side it displays a ploty graphic of the average composition.

```{r flexdash_kirby21, echo=TRUE, warning=FALSE, eval=TRUE}

# library(flexdashboard)
kirb_raw=("https://raw.githubusercontent.com/neuroconductor/kirby21.mricloud/master/inst/visit_1/127/kirby_3_1_ax_283Labels_M2_corrected_stats.txt")
dat_kirby=readSubject(kirb_raw)

dat11=dat_kirby[[1]]
dat12=dat_kirby[[2]]
dat13=dat_kirby[[3]]
dat14=dat_kirby[[4]]
dat15=dat_kirby[[5]]
dat21=dat_kirby[[6]]
dat22=dat_kirby[[7]]
dat23=dat_kirby[[8]]
dat24=dat_kirby[[9]]
dat25=dat_kirby[[10]]


 fina_mat_2=dat11 %>% select(roi, volume) %>%
  mutate(intrac_volume=sum(volume)) %>%
  mutate(intr_lessCSF=sum(volume[roi!="CSF"])) %>%
  mutate(propo_intra=round((volume/intr_lessCSF*100),2))
 
plotprop2=ggplotly(ggplot(fina_mat_2, aes(x=roi,y=propo_intra,fill=roi))+geom_bar(stat="identity")+theme(axis.text.x=element_text(angle = 90)))
plotprop2

inputPanel(
  selectInput("type", label = "Type of brain summary:",
              choices = c(1,2), selected = 1),

  # sliderInput("type", label = "Type of brain summary:",
  #             min = 1, max = 2, value = 1, step = 1),

  sliderInput("level", label = "Level of summary:",
              min = 1, max = 3, value = 1, step = 1),
  # 
  # numericInput("type", "Type of brain summary required:", 2, min = 1, max = 2, step=1),
  # verbatimTextOutput("data_vect1"),
  # 
  # numericInput("level", "Level of brain summary required:", 3, min = 1, max = 2, step=1),
  # verbatimTextOutput("data_vect2"),
  
  plotOutput("plotly22"),
  verbatimTextOutput("data_vect1"),
    verbatimTextOutput("data_vect2")

)

# 
# data_vector=as.matrix.data.frame(as.integer((reactive({
#     c(input$type, input$level)
#   }))))


renderPlot({
  
  output$data_vect1 <- renderText({ input$type })
  output$data_vect2 <- renderText({ input$level })
  
# dat_mat=as.matrix.data.frame(input$type, input$level, nrow=2, byrow=TRUE)
# output$data_vect1=abs((input$type))
# output$data_vect2=abs((input$level))

  
  dat_mat=as.matrix.noquote(as.matrix.data.frame((c(output$data_vect1, output$data_vect2))))
 
   colnames(dat_mat)[colnames(data) == "V1"] <- "input_vect"
  
  if (data_mat$input_vect[1,]==1 && data_mat$input_vect[2,]==1) {
    fina_mat=dat11
  }
    if (data_mat$input_vect[1,]==1 && data_mat$input_vect[2,]==2) {
    fina_mat=dat12
  }
    if (data_mat$input_vect[1,]==1 && data_mat$input_vect[2,]==3) {
    fina_mat=dat13
  }
  
  #   if (data_mat[1,]==1 && data_mat[2,]==4) {
  #   fina_mat=dat14
  # }
  #   if (data_mat[1,]==1 && data_mat[2,]==5) {
  #   fina_mat=dat15
  # }

    if (data_mat$input_vect[1,]==2 && data_mat$input_vect[2,]==1) {
    fina_mat=dat21
  }
    if (data_mat$input_vect[1,]==2 && data_mat$input_vect[2,]==2) {
    fina_mat=dat22
  }
  
    if (data_mat$input_vect[1,]==2 && data_mat$input_vect[2,]==3) {
    fina_mat=dat23
    }
  
  # 
  #   if (data_mat[1,]==2 && data_mat[2,]==4) {
  #   fina_mat=dat23
  # }
  # 
  # if (data_mat[1,]==2 && data_mat[2,]==5) {
  #   fina_mat=dat23
  # }
  
  fina_mat_1= fina_mat %>% select(roi, volume) %>%
  mutate(intrac_volume=sum(volume)) %>%
  mutate(intr_lessCSF=sum(volume[roi!="CSF"])) %>%
  mutate(propo_intra=round((volume/intr_lessCSF*100),2))

# 
  
   
plotOutput$plotOutput=ggplotly(ggplot(fina_mat_1, aes(x=roi,y=propo_intra,fill=roi))+geom_bar(stat="identity")+theme(axis.text.x=element_text(angle = 90)))

})




```




Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.


